Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2011-02-09 paper/main.tex
Added automated conversion from .dia to proper .pdf in Makefile
Added alignment runtime plot
testing merge.  started on lit review

@@

@@

\section{ALM Algorithm}
%Describe the two variants of the ALM algorithm

>>>>

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/pipeline.pdf}
\caption{The Full Recognition Pipeline}
\label{fig:pipeline}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/alignment_l1.pdf}
\caption{Alignment Stage L1 Solver}
\label{fig:alignment_l1}
\end{figure}

@@

Past work in parallelizing $\ell_1$-minimization has been limited.  Murphy at UCB implemented the L1-Spirit algorithm on Nvidia GPUs for MRI reconstruction and Borghi at UCLA developed a proximal based algorithm using Moreau-Yosida regularization.

In a review paper by Allen Yang, they list 5 fast methods that solve $\ell_1$-minimization including gradient projection, homotopy, iterative shrinkage-thresholding, proximal gradient, and augmented lagrangian methods.  According to the review paper, they have determined that Homotopy and the Augmented Lagrangian Multiplier methods achieve the best recognition rates while maintaining a low computational cost.  A closer look at these two algorithms will show that

@@

\section{Augmented Lagrangian Multiplier Algorithm}
%Describe the two variants of the ALM algorithm
